### 2019-09-13 README.Rmd
added step numbers and detaile figure legend to Figure 1

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
) 
```
# diffEnrich

@@

```{r, echo=FALSE, fig.cap='Figure 1. diffEnrich analysis pipeline.', dpi=400}
suppressMessages(library(diagram))

@@

## Build flow chart
for (i in 1:nr){
  arrpos[i, ] <- straightarrow (to = elpos[fromto[i, 2], ],
                                from = elpos[fromto[i, 1], ],
                                lwd = 2, arr.pos = 0.6, arr.length = 0.5)
  textellipse(elpos[1,], 0.10, 0.04, lab = "geneList1", box.col = "purple",
              shadow.col = "purple4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[2,], 0.10, 0.03, lab = "get_kegg()", box.col = "steelblue1",
              shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[3,], 0.10, 0.04, lab = "geneList2", box.col = "purple",
              shadow.col = "purple4", shadow.size = 0.005, cex = 1.0)
  textround(elpos[4,], 0.10, 0.03,lab = "KEGG REST API", box.col = "orange1",
            shadow.col = "orange4", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[5,], 0.15, 0.04, lab = c("cleaned gene-to-pathway", "map"), box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[6,], 0.10, 0.03,lab = "pathEnrich(List 1)", box.col = "steelblue1",
            shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[7,], 0.10, 0.03, lab = "pathEnrich(List 2)", box.col = "steelblue1",
           shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[8,], 0.10, 0.04, lab = c("pathEnrich","result/object"), box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[9,], 0.10, 0.04, lab = c("pathEnrich","result/object"),box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[10,], 0.10, 0.03, lab = "diffEnrich()", box.col = "steelblue1",
           shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[11,], 0.10, 0.04, lab = c("diffEnrich","result/object"), box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[12,], 0.11, 0.03, lab = "plotFoldEnrichment", box.col = "steelblue1",
           shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  text(0.15,0.05, "Figure 1. diffEnrich Analysis pipeline", cex = 0.75)
}
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval.after = 'fig.cap'
) 
```
# diffEnrich

@@

```{r, echo=FALSE, fig.cap=cap, dpi=400}
suppressMessages(library(diagram))

@@

## Build flow chart
for (i in 1:nr){
  arrpos[i, ] <- straightarrow (to = elpos[fromto[i, 2], ],
                                from = elpos[fromto[i, 1], ],
                                lwd = 2, arr.pos = 0.6, arr.length = 0.5)
  textellipse(elpos[1,], 0.10, 0.04, lab = "geneList1", box.col = "purple",
              shadow.col = "purple4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[2,], 0.10, 0.03, lab = "get_kegg()", box.col = "steelblue1",
              shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[3,], 0.10, 0.04, lab = "geneList2", box.col = "purple",
              shadow.col = "purple4", shadow.size = 0.005, cex = 1.0)
  textround(elpos[4,], 0.10, 0.03,lab = "KEGG REST API", box.col = "orange1",
            shadow.col = "orange4", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[5,], 0.15, 0.04, lab = c("cleaned gene-to-pathway", "map"), box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[6,], 0.10, 0.03,lab = "pathEnrich(List 1)", box.col = "steelblue1",
            shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[7,], 0.10, 0.03, lab = "pathEnrich(List 2)", box.col = "steelblue1",
           shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[8,], 0.10, 0.04, lab = c("pathEnrich","result/object"), box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[9,], 0.10, 0.04, lab = c("pathEnrich","result/object"),box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[10,], 0.10, 0.03, lab = "diffEnrich()", box.col = "steelblue1",
           shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  textellipse(elpos[11,], 0.10, 0.04, lab = c("diffEnrich","result/object"), box.col = "firebrick1",
              shadow.col = "firebrick4", shadow.size = 0.005, cex = 1.0)
  textrect(elpos[12,], 0.11, 0.03, lab = "plotFoldEnrichment", box.col = "steelblue1",
           shadow.col = "darkblue", shadow.size = 0.005, cex = 1.0)
  # text(0.15,0.05, "Figure 1. diffEnrich Analysis pipeline", cex = 0.75)
  text(0.05,0.87, "Step 1", cex = 1.2, font = 2)
  text(0.05,0.57, "Step 2", cex = 1.2, font = 2)
  text(0.05,0.35, "Step 3", cex = 1.2, font = 2)
  text(0.05,0.10, "Step 4", cex = 1.2, font = 2)
}

cap <- c("Figure 1. diffEnrich Analysis pipeline. Functions within the diffEnrich package are represented by blue rectangles. The data that must be provided by the user is represented by the pruple ovals. Data objects generated by a function in diffEnrich are representaed by red ovals. The external call of the get_kegg function to the KEGG REST API is represented in yellow.")
```
